Analysis_manuscript_mash_GxE

### 2020-11-19 R/Analysis_manuscript_mash_GxE.Rmd
Add mash analysis with Mashattan by covariance matrix and other allele features

#' @param posterior_weights Vector containing the posterior
#'     probability of each mixture component in Ulist for the data.
```{r}
length(get_significant_results(m))
get_significant_results(m)[1:10]
get_significant_results(m)[1:10]

@@

n=7500
i = get_significant_results(m)[n]

@@

Gulf
```{r}
inputdir <- file.path("../analysis/gwas/BLUPs/single_sites", "Gulf")
mash_out <- pvdiv_results_in_folder(inputdir, "Strong")
mash_out
m <- read_rds(file.path(inputdir, mash_out[11]))
mash_plot_covar(m, saveoutput = TRUE)
get_U_by_mass(m)
mash_plot_Ulist(m, range = get_U_by_mass(m))
mash_plot_effects(m, n = 1, saveoutput = TRUE)
mash_plot_sig_by_condition(m, saveoutput = TRUE)
mash_plot_manhattan_by_condition(m, saveoutput = TRUE)
mash_plot_pairwise_sharing(effectRDS = file.path(inputdir, mash_out[1])) # sign
mash_plot_pairwise_sharing(effectRDS = file.path(inputdir, mash_out[2])) # sign & size
Gulf_greenup_gxe <- get_GxE(m)

>>>>

@param posterior_weights Vector containing the posterior
     probability of each mixture component in Ulist for the data.
```{r}
length(get_significant_results(m))
get_significant_results(m)[1:10]
get_significant_results(m)[1:10]

@@

n=1
i = get_significant_results(m)[n]

@@

## Load m for Gulf
```{r}
inputdir <- file.path("../analysis/gwas/BLUPs/single_sites", "Gulf")
mash_out <- pvdiv_results_in_folder(inputdir, "Strong")
mash_out
m <- read_rds(file.path(inputdir, mash_out[11]))
```

Mashhattan where points are colored by which covariance matrix they load most strongly on to. Do different regions of the genome have distinct patterns, or are they all jumbled up?
```{r}

  log10bf_df <- switchgrassGWAS:::get_log10bf(m = m) %>%
    as.data.frame() %>%
    rownames_to_column(var = "value") %>%
    mutate(value = as.integer(.data$value)) %>%
    as_tibble() %>%
    left_join(switchgrassGWAS:::get_marker_df(m = m), by = "value") %>%
    dplyr::rename(log10BayesFactor = .data$V1) %>%
    dplyr::select(-.data$value)

#' Return the Bayes Factor for each effect
#'
#' @param m the mash result (from joint or 1by1 analysis); must have been
#'     computed using usepointmass=TRUE
#'
#' @return if m was fitted using usepointmass=TRUE then returns a vector of
#'     the log10(bf) values for each effect. That is, the jth element
#'     lbf_j is log10(Pr(Bj | g=ghat-nonnull)/Pr(Bj | g = 0)) where gha
#'     t-nonnull is the non-null part of ghat.  Otherwise returns NULL.
#'
get_log10bf = function(m) {
  if(is.null(m$null_loglik)){
    return(NULL)
  } else {
    return((m$alt_loglik - m$null_loglik)/log(10))
  }
}

#' Return the name of the covariance matrix with the highest posterior weight
#'     for each effect
#'
#' @param m the mash result (from joint or 1by1 analysis)
#'
#' @return returns a df with Marker, Covariance_Matrix, and Grid_Value. I'm assuming that the grid value is an indication of like a svd decomp
#'
get_topcov = function(m) {
  df <- switchgrassGWAS:::get_marker_df(m = m)
  covdf <- purrr::map_chr(df$value, ~ names(which(m$posterior_weights[.x,] ==
                                           max(m$posterior_weights[.x,])))) %>%
    enframe(name = "value", value = "Covariance_Grid") %>%
    separate("Covariance_Grid", into = c("Covariance_Matrix", "Grid_Value"),
             sep = "\\.", remove = FALSE) 
  df <- df %>% full_join(covdf, by = "value")
  return(df)
  }

names(which(m$posterior_weights[i,] == max(m$posterior_weights[i,])))

  ggman_df <- df %>%
    separate(.data$Marker, into = c("Chr", "Pos"), remove = FALSE, sep = "_",
             extra = "merge", convert = TRUE) %>%
    left_join(log10bf_df, by = "Marker") %>%
    arrange(.data$Chr, .data$Pos) %>%
    group_by(Covariance_Grid) %>% add_tally() %>%
    arrange(desc(n))

  log10BF <- expression(paste("log"[10], plain("(Bayes Factor)")))

  ggmanobject <- ggplot(data = ggman_df, aes(x = .data$Pos, y = .data$log10BayesFactor)) +
    switchgrassGWAS::theme_oeco +
    geom_point(aes(color = .data$Covariance_Grid, fill = .data$Covariance_Grid,
                   shape = as.factor(.data$Chr))) +
    facet_wrap(~ .data$Chr, nrow = 1, scales = "free_x", strip.position = "bottom") +
    scale_color_viridis_d(option = "D", end = 0.95) + scale_fill_viridis_d(option = "D", end = 0.95) +
    theme(strip.text = element_text(size = 8),
          axis.text.y = element_text(size = 8),
          axis.text.x = element_blank(),
          legend.text = element_text(size = 8),
          axis.ticks.x = element_blank(),
          panel.background = element_rect(fill=NA)) +
    labs(x = "Chromosome", y = log10BF) +
    scale_x_continuous(expand = c(0.32, 0.32)) +
    scale_shape_manual(values = rep(c(21,22),9), guide = FALSE) +
    geom_hline(yintercept = 2, linetype = 2)
```

```{r}

mash_plot_covar(m, saveoutput = TRUE)
get_U_by_mass(m)
mash_plot_Ulist(m, range = get_U_by_mass(m))
mash_plot_effects(m, n = 1, saveoutput = TRUE)
mash_plot_sig_by_condition(m, saveoutput = TRUE)
mash_plot_manhattan_by_condition(m, saveoutput = TRUE)
mash_plot_pairwise_sharing(effectRDS = file.path(inputdir, mash_out[1])) # sign
mash_plot_pairwise_sharing(effectRDS = file.path(inputdir, mash_out[2])) # sign & size
Gulf_greenup_gxe <- get_GxE(m)
